Brownian Dynein Model

### 2016-08-27 latex/paper.tex
Add first half of new onebound derivation.

\section{One bound}

@@

In the one-bound case, we use four angles, as illustrated in
Fig.~\ref{fig:onebound}.

>>>>

\section{Onebound}

@@

First, some definitions...
\begin{align*}
F_{bmx} &= \frac{f_{bmx} + R_{bmx}}{\gamma}\\
F_{xt } &= \frac{f_{xt} + R_{xt}}{\gamma}\\
...\\
X_{bs} &= \frac{X_{bm} - X_{bb}}{\gamma}\\
X_{bt} &= \frac{X_t - X_{bm}}{\gamma}\\
...\\
\end{align*}

\subsection{Brownian Dynamics equations}
\begin{align*}
  \dot{X}_{bm} &= F_{bmx} - \gm\lambda_{bs}X_{bs} + \gm\lambda_{bt}X_{bt}\\
  \dot{X}_{t}  &= F_{tx}  - \gt\lambda_{bt}X_{bt} + \gt\lambda_{ut}X_{ut}\\
  \dot{X}_{um} &= F_{umx} - \gm\lambda_{ut}X_{ut} + \gm\lambda_{us}X_{us}\\
  \dot{X}_{ub} &= F_{ubx} - \gb\lambda_{us}X_{us}
\end{align*}

\begin{align*}
  \dot{Y}_{bm} &= F_{bmx} - \gm\lambda_{bs}Y_{bs} + \gm\lambda_{bt}Y_{bt}\\
  \dot{Y}_{t}  &= F_{tx}  - \gt\lambda_{bt}Y_{bt} + \gt\lambda_{ut}Y_{ut}\\
  \dot{Y}_{um} &= F_{umx} - \gm\lambda_{ut}Y_{ut} + \gm\lambda_{us}Y_{us}\\
  \dot{Y}_{ub} &= F_{ubx} - \gb\lambda_{us}Y_{us}
\end{align*}

\subsection{Expanded velocities}

\begin{align*}
\dot{X}_{bm} &= -L_s\sin(\theta_{bb})\dot{\theta}_{bb}\\
\dot{X}_{t } &= -L_s\sin(\theta_{bb})\dot{\theta}_{bb} - L_t\sin(\theta_{bm})\dot{\theta}_{bm}\\
\dot{X}_{um} &= -L_s\sin(\theta_{bb})\dot{\theta}_{bb} - L_t\sin(\theta_{bm})\dot{\theta}_{bm} + L_t\sin(\theta_{um})\dot{\theta}_{um}\\
\dot{X}_{ub} &= -L_s\sin(\theta_{bb})\dot{\theta}_{bb} - L_t\sin(\theta_{bm})\dot{\theta}_{bm} + L_t\sin(\theta_{um})\dot{\theta}_{um} + L_s\sin(\theta_{ub})\dot{\theta}_{ub}\\
\end{align*}

\begin{align*}
\dot{Y}_{bm} &= L_s\cos(\theta_{bb})\dot{\theta}_{bm}\\
\dot{Y}_{t } &= L_s\cos(\theta_{bb})\dot{\theta}_{bb} + L_t\cos(\theta_{bm})\dot{\theta}_{bm}\\
\dot{Y}_{um} &= L_s\cos(\theta_{bb})\dot{\theta}_{bb} + L_t\cos(\theta_{bm})\dot{\theta}_{bm} - L_t\cos(\theta_{um})\dot{\theta}_{um}\\
\dot{Y}_{ub} &= L_s\cos(\theta_{bb})\dot{\theta}_{bb} + L_t\cos(\theta_{bm})\dot{\theta}_{bm} - L_t\cos(\theta_{um})\dot{\theta}_{um} - L_s\cos(\theta_{ub})\dot{\theta}_{ub}\\
\end{align*}

\subsection{System of Equations}
Now to create our system of equations, we combine the Brownian equations with our expanded velocities. This system of equations takes into account both the dynamics of Brownian Mechanics (from the BD equations) as well as the constraints of our coordinate system (from the velocity expansions).

\begin{align*}
F_{bmx} - \gm\lambda_{bs}X_{bs} + \gm\lambda_{bt}X_{bt} &= -L_s\sin(\theta_{bb})\dot{\theta}_{bb}\\
F_{tx}  - \gt\lambda_{bt}X_{bt} + \gt\lambda_{ut}X_{ut} &= -L_s\sin(\theta_{bb})\dot{\theta}_{bb} - L_t\sin(\theta_{bm})\dot{\theta}_{bm}\\
F_{umx} - \gm\lambda_{ut}X_{ut} + \gm\lambda_{us}X_{us} &= -L_s\sin(\theta_{bb})\dot{\theta}_{bb} - L_t\sin(\theta_{bm})\dot{\theta}_{bm} + L_t\sin(\theta_{um})\dot{\theta}_{um}\\
F_{ubx} - \gb\lambda_{us}X_{us} &= -L_s\sin(\theta_{bb})\dot{\theta}_{bb} - L_t\sin(\theta_{bm})\dot{\theta}_{bm} + L_t\sin(\theta_{um})\dot{\theta}_{um} + L_s\sin(\theta_{ub})\dot{\theta}_{ub}\\
\\
F_{bmy} - \gm\lambda_{bs}Y_{bs} + \gm\lambda_{bt}Y_{bt} &= L_s\cos(\theta_{bb})\dot{\theta}_{bm}\\
F_{ty}  - \gt\lambda_{bt}Y_{bt} + \gt\lambda_{ut}Y_{ut} &= L_s\cos(\theta_{bb})\dot{\theta}_{bb} + L_t\cos(\theta_{bm})\dot{\theta}_{bm}\\
F_{umy} - \gm\lambda_{ut}Y_{ut} + \gm\lambda_{us}Y_{us} &= L_s\cos(\theta_{bb})\dot{\theta}_{bb} + L_t\cos(\theta_{bm})\dot{\theta}_{bm} - L_t\cos(\theta_{um})\dot{\theta}_{um}\\
F_{uby} - \gb\lambda_{us}Y_{us} &= L_s\cos(\theta_{bb})\dot{\theta}_{bb} + L_t\cos(\theta_{bm})\dot{\theta}_{bm} - L_t\cos(\theta_{um})\dot{\theta}_{um} - L_s\cos(\theta_{ub})\dot{\theta}_{ub}\\
\end{align*}

\subsection{Matrix form}

\[
\hspace{-2.5cm}
\begin{pmatrix}
  L_s\sin\theta_{bb} & 0 & 0 & 0 & -\gm X_{bs} & \gm\lambda_{bt}X_{bt} & 0 & 0\\
  L_s\sin(\theta_{bb}) & L_t\sin(\theta_{bm}) & 0 & 0 & 0 & -\gt X_{bt} & \gt X_{ut} & 0\\
  L_s\sin(\theta_{bb}) & L_t\sin(\theta_{bm}) & -L_t\sin(\theta_{um}) & 0 & 0 & 0 & -\gm X_{ut} & \gm X_{us}\\
  L_s\sin(\theta_{bb}) & L_t\sin(\theta_{bm}) & -L_t\sin(\theta_{um}) & -L_s\sin(\theta_{ub}) & 0 & 0 & 0 & -\gb X_{us}\\
  -L_s\cos(\theta_{bb}) & 0 & 0 & 0 & -\gm Y_{bs} & \gm Y_{bt} & 0 & 0\\
  -L_s\cos(\theta_{bb}) & -L_t\cos(\theta_{bm}) & 0 & 0 & 0 & -\gt Y_{bt} & \gt Y_{ut} & 0\\
  -L_s\cos(\theta_{bb}) & -L_t\cos(\theta_{bm}) & L_t\cos(\theta_{um}) & 0 & 0 & 0 & -\gm Y_{ut} & \gm Y_{us}\\
  -L_s\cos(\theta_{bb}) & -L_t\cos(\theta_{bm}) & L_t\cos(\theta_{um}) & L_s\cos(\theta_{ub}) & 0 & 0 & 0 & -\gb Y_{us}\\
\end{pmatrix}
\begin{pmatrix}
  \dot{\theta}_{bb}\\
  \dot{\theta}_{bm}\\
  \dot{\theta}_{um}\\
  \dot{\theta}_{ub}\\
  \lambda_{bs}\\
  \lambda_{bt}\\
  \lambda_{ut}\\
  \lambda_{us}\\
\end{pmatrix}
=
\begin{pmatrix}
  -F_{bmx}\\
  -F_{tx}\\
  -F_{umx}\\
  -F_{ubx}\\
  -F_{bmy}\\
  -F_{ty}\\
  -F_{umy}\\
  -F_{uby}\\
\end{pmatrix}
\]

\subsection{Mathematica input}
The above matrix equation can be represented as follows and solved via Mathematica:

\begin{align*}
AA &= L_s\sin\theta_{bb}      &  LL &= -L_s\cos(\theta_{bb})\\
BB &= L_t\sin(\theta_{bm})    &	 MM &= -L_t\cos(\theta_{bm})\\
CC &= -L_t\sin(\theta_{um})   &	 NN &= L_t\cos(\theta_{um})\\
DD &= -L_s\sin(\theta_{ub})   &	 OO &= L_s\cos(\theta_{ub})\\
\\
EE &= -\gm X_{bs}       &    PP &= -\gm Y_{bs}\\
FF &= \gm X_{bt}	    &	 QQ &= \gm Y_{bt}\\ 
GG &= -\gt X_{bt}	    &	 RR &= -\gt Y_{bt}\\
HH &= \gt X_{ut}	    &	 SS &= \gt Y_{ut}\\ 
II &= -\gm X_{ut}	    &	 TT &= -\gm Y_{ut}\\
JJ &= \gm X_{us}	    &	 UU &= \gm Y_{us}\\ 
KK &= -\gb X_{us}       &	 VV &= -\gb Y_{us}\\
\end{align*}

\[
\begin{pmatrix}
  AA & 0 & 0 & 0 & EE & FF & 0 & 0\\
  AA & BB & 0 & 0 & 0 & GG & HH & 0\\
  AA & BB & CC & 0 & 0 & 0 & II & JJ\\
  AA & BB & CC & DD & 0 & 0 & 0 & KK\\
  LL & 0 & 0 & 0 & PP & QQ & 0 & 0\\
  LL & MM & 0 & 0 & 0 & RR & SS & 0\\
  LL & MM & NN & 0 & 0 & 0 & TT & UU\\
  LL & MM & NN & OO & 0 & 0 & 0 & VV\\
\end{pmatrix}
V
=
\begin{pmatrix}
  X1\\
  X2\\
  X3\\
  X4\\
  X5\\
  X6\\
  X7\\
  X8\\
\end{pmatrix}
\]
